### 2020-01-30 README.Rmd
Cleaned up README a bit

**EDA of both BigWoods & SCBI*: Note the large variation in growths for the SCBI trees over the BigWoods trees.

@@

@@

* Define the blocking structure
* Determine the degree of spatial autocorrelation for various `max_dist` values

```{r}
# spatial blocking by specified range with random assignment

```

* If the above doesn't work, the go back to what we used for PLOS paper.
* Consider making `growth_df` an `sf` object

@@

# Buffer polygon
bw_buffer <- bw_boundary %>%
  st_buffer(dist = -25)

@@

>>>>

**EDA of both BigWoods & SCBI**: Note the large variation in growths for the SCBI trees over the BigWoods trees.

@@

#### Defining buffers

@@

@@

# Buffer polygon
bw_buffer <- bw_boundary %>%
  st_buffer(dist = -max_dist)

@@

#### Spatial cross-validation

* Define the blocking structure
* Determine the degree of spatial autocorrelation for various `max_dist` values
* If the above doesn't work, the go back to what we used for PLOS paper.
